---
title: "Aho_livesession4assignment"
author: "Andy Ho"
date: "June 2, 2018"
output: html_document
---

#### 1. FiveThirtyEight Data set : College of All Ages
* A. Install the fivethirtyeight package.
```{r}
library(fivethirtyeight)
```

* B. Assign eighteenth data set to 'df'
```{r}
data("college_all_ages")
df <- college_all_ages [18,]
head(df)
```

* C. Write out URL in a comment to the related news story
```{r}
vignette("fivethirtyeight", all = FALSE)
```
#####Related News Story for college_all_ages data set
The raw data behind the story "The Economic Guide To Picking A College Major"</br>
URL: https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/.

* D. Dimensions and column names of this data frame.
```{r}
dim(college_all_ages)
names (college_all_ages)
```

#### 2. Data Summary
+ A. R Code for column names of the data frame.
```{r}
colnames(college_all_ages)
ncol(college_all_ages)
```

+ B. A count of each unique major_category in df.
```{r}
x <- college_all_ages$major_category
major_count <- aggregate(data.frame(count = x), list(major_category = x), length)
major_count
```

+ C. Barplot of major_count
```{r}
barplot(major_count$count, names = major_count$major_category, xlab = "Count", ylab = "Major", main = 'Major Count', col = 'blue', horiz = TRUE, las = 2)
```

+ D. Output fivethirtyeight data to csv file.  <b>Refer to College_All_Ages.csv attachment.</b>
```{r}
write.csv(college_all_ages, file = "College_All_Ages.csv", row.names = FALSE)
```

#### 3. Codebook
* A. Github URL: https://github.com/atho316/MSDS6306-Homework

* B. README.md file created for main Homework repo and also for each nested homework directory.

* C. All of following files are loaded to nested directory under MSDS6306-Homework in Github
     + Aho_livesession4assignment.Rmd
     + Aho_livesession4assignment.html
     + Aho_Swirl_04.txt
     + College_All_Ages.csv
     + ReadMe.md

* D. Github URL: https://github.com/atho316/MSDS6306-Homework/tree/Unit-04


#### 4. Swirl
+ Refer to Aho_Swirl_04.txt

  
